---
title: "Simple document"
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Load the airbnb data

```{r}
data("nyc_airbnb")
nyc_airbnb %>% slice(1:1000)
nyc_airbnb %>% sample_n(1000) # view 1000 random rows of my dataset
nyc_airbnb %>% sample_frac(size = .1)# view 10% of my dataset
```

## Brainstorm some questions

* what is the best Airbnb in staten island for < $100
* what price range is popular in each borough
* what apartment features are related to price
* cheapest room type in each neighborhood
* host have higher ratings

## Answer some question

##  what price range in each neighborhood (my idea)
```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group) %>% 
  summarize(min_price = min(price),
            max_price = max(price))
```

```{r}
nyc_airbnb =
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2)

```

```{r}
nyc_airbnb %>% 
  count(neighbourhood_group, room_type) %>% 
  pivot_wider(names_from = room_type, values_from = n)
```

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarize(mean_price = mean(price))
```

```{r}
##fct_reorder(被relevel的对象, relevel的新依据))
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  count(neighbourhood)
  
nyc_airbnb %>% 
  filter(
    price < 1000,
    neighbourhood_group == "Manhattan") %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip() #颠倒x，y axis
```


```{r}
nyc_airbnb %>% 
  sample_n(1000) %>% 
  ggplot(aes(x = lat, y =long, color = price)) +
  geom_point()
```


## build a interactive map :https://teachdatascience.com/leaflet/
## https://rstudio.github.io/leaflet/
## create a leaflet map

```{r}
pal <- colorNumeric("viridis", nyc_airbnb %>% pull(stars))

nyc_airbnb %>% 
  sample_n(10) %>%
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(~lat, ~long)

nyc_airbnb %>% 
  sample_n(10) %>%
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addMarkers(~lat, ~long)

nyc_airbnb %>% 
  drop_na(stars) %>% 
  sample_n(1000) %>%
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1, color =~ pal(stars))
```



