---
title: "Exploratory analysis"
output: html_document
---

```{r}
library(tidyverse)
library(patchwork)
```


```{r, eval = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Load the weather data

```{r}
#lubridate::floor_date(date, unit = "month"))就是把date round到最近的month里，这样2017-01-10在一个新的叫month的variable里就变成2017-01-01
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10,
    month = lubridate::floor_date(date, unit = "month")) %>%
  select(name, id, everything())

weather_df
```


## `group_by`

```{r}
weather_df %>% 
  group_by(name, month) %>% 
  ungroup(month)
```

## counting things

count month/name observations

```{r}
weather_df %>% 
  group_by(month) %>% 
  summarize(n_obs =n())

weather_df %>% 
  group_by(name, month) %>% 
  summarize(n_obs =n())
```

we can use `count()` as well

```{r}
#name = "n_obs" means 给counts命名为n_obs
weather_df %>% 
  count(month, name = "n_obs")
```

***Never*** use base R's table function
不要用table function方法进行counting，如下
```{r}
weather_df %>% 
  pull(month) %>% 
  table()
```

other helpful counters

```{r}
#n_days = n_distinct(date)使用来计算每个month里有多少unique date
weather_df %>% 
  group_by(month) %>% 
  summarize(
    n_obs =n(),
    n_days = n_distinct(date))
```

## A digression on 2X2 tables

```{r}
#case_when(条件 ~ output) function means given this condition, then output.
#TRUE ~ "" means :if I miss something, just put as missing value
weather_df %>% 
  filter(name !="Waikiki_HA") %>% 
  mutate(
    cold = case_when(
      tmax < 5 ~ "cold",
      tmax >= 5 ~ "not_cold",
      TRUE ~ ""
    )
  ) %>% 
  group_by(name, cold) %>% 
  summarize(count = n())
```

```{r}
#janitor::tabyl()可以得到跟上面一样的结果，只是这个是2X2的table，会把括号里variable里面不同项（labels）拆开成不同的列
weather_df %>% 
  filter(name !="Waikiki_HA") %>% 
  mutate(
    cold = case_when(
      tmax < 5 ~ "cold",
      tmax >= 5 ~ "not_cold",
      TRUE ~ ""
    )
  ) %>% 
  janitor::tabyl(name, cold)
```

## General summaries

You can do lots of summaries.

```{r}
#na.rm = TRUE :remove NA
weather_df %>% 
  group_by(name, month) %>% 
  summarize(
    mean_tmax = mean(tmax, na.rm = TRUE),
    mean_prcp = mean(prcp, na.rm = TRUE),
    median_tmin = median(tmin, na.rm = TRUE)
  )
```

This is a dataframe! So we can make a plot

```{r}
#na.rm = TRUE :remove NA
weather_df %>% 
  group_by(name, month) %>% 
  summarize(
    mean_tmax = mean(tmax, na.rm = TRUE),
    mean_prcp = mean(prcp, na.rm = TRUE),
    median_tmin = median(tmin, na.rm = TRUE)
  ) %>% 
  ggplot(aes(x = month, y = mean_tmax, color = name)) +
  geom_line()
```

Suppose you want to sumarize many columns.

```{r}
#一次性summarize多个variables（column的数据
weather_df %>% 
  group_by(name, month) %>% 
  summarize(across(prcp:tmin, mean))
```

Reminder sometimes your results are easier to read in another format.

```{r}
#   knitr::kable(digits = x): format something is easier to read if you have r markdown doc,digits = x是保留几位小数。 总的来说就是把dataframe变成容易读的表格

weather_df %>% 
  group_by(name, month) %>% 
  summarize(mean_tmax = mean(tmax)) %>% 
  pivot_wider(
    names_from = name,
    values_from = mean_tmax
  ) %>% 
  knitr::kable(digits = 1)
```


`group_by` amd `mutate`

```{r}
weather_df %>% 
  group_by(name) %>% 
  mutate(
    mean_tmax = mean(tmax, na.rm = TRUE),
    centered_tmax = tmax - mean_tmax
  ) %>% 
  ggplot(aes(x = date, y = centered_tmax, color = name)) +
  geom_point()
```

what about window functions

ranking...

```{r}
#min_rank: a way to define ranks,在这里就是每个地区每个月的tmax排名
#此时是正序，温度越低rank越小
weather_df %>% 
  group_by(name, month) %>% 
  mutate(temp_rank = min_rank(tmax))

###此时是降序，温度越低rank越大
weather_df %>% 
  group_by(name, month) %>% 
  mutate(temp_rank = min_rank(desc(tmax)))
```
lag

```{r}
#lag : find the previous values in a vector, 而且可以限制从第几个开始才lag
#比如在这里，5代表空开前五个才开始lag，就是说row6 lag_temp显示的是row1 tmax的数据
weather_df %>% 
  group_by(name) %>% 
  mutate(lag_temp = lag(tmax, 5))

#我们可以利用lag得到前后项相减的结果
weather_df %>% 
  group_by(name) %>% 
  mutate(temp_change = tmax - lag(tmax))

#总结每个地区前后两天温差相差最高是多少
weather_df %>% 
  group_by(name) %>% 
  mutate(temp_change = tmax - lag(tmax)) %>% 
  summarize(
    temp_change_max = max(temp_change, na.rm = TRUE),
    temp_change_sd = sd(temp_change, na.rm = TRUE)
  )
```

